Untitled

### 2014-10-19 TrialFile.Rmd
Reverted to bullets for proposal document

map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
    col="gray90", fill=TRUE)
```

>>>>

map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
    col="gray90", fill=TRUE)

### Need a map of 3 kinds of welfare states
### Scandanavian
### Market oriented (UK)
### France/Germany - state established historical welfare state

```
